This report presents \emph{NDSwin-JAX}, a JAX/Flax implementation of the Swin Transformer that was refactored into a genuinely N-dimensional framework. The core engineering objective was to preserve the shifted-window design of the original Swin architecture while removing its hard dependency on 2D image grids. In practice, that meant rewriting patch embedding, window partitioning and reversal, cyclic shifting, relative position indexing, and hierarchical stage composition so that they operate on arbitrary spatial dimensionalities controlled only by configuration.

The resulting system was evaluated on the latest complete queue run preserved in the repository: 2D classification on CIFAR-10 and 3D voxel classification on a ModelNet40 export. The project also includes a CLI-driven workflow for training, random-search sweeps, and queue-based orchestration, so the evaluation covers both model behavior and the reproducibility of the surrounding experimentation pipeline. The saved April 1, 2026 artifacts show that the same codebase can complete a 48-trial CIFAR-10 sweep, a 15-trial ModelNet40 sweep, and full retraining of the best configuration for each dataset. Within that kept evidence, the best sweep validation accuracies reach \(0.7438\) on CIFAR-10 and \(0.8092\) on ModelNet40, while the corresponding final retraining runs restore checkpoints with validation accuracies of \(0.7334\) and \(0.7573\).

These results are sufficient to support the central claim of the project: the implementation successfully generalizes shifted-window transformers beyond 2D and remains trainable on both image and voxel inputs under a shared software stack. At the same time, the report stays conservative about what the saved evidence does \emph{not} show. The repository snapshot contains validation metrics only, not held-out test measurements. It also contains no repeated-seed experiments, no error bars, and no statistical significance tests. Consequently, the contribution is best understood as a traceable implementation and empirical validation study rather than a definitive benchmark claim against published Swin baselines.
