The conceptual starting point of this work is the Swin Transformer of Liu et al.\ \cite{liu2021swin}. Swin introduced a hierarchical transformer backbone in which self-attention is restricted to non-overlapping local windows, while a cyclic window shift between consecutive blocks restores cross-window communication. This combination preserves locality, improves scalability, and provides a natural multistage structure through patch merging and progressively increased channel width. The present project retains those ideas, but reimplements them so that the same operators apply to arbitrary spatial dimensionalities rather than to 2D image grids only.

On the software side, the project is built in JAX and Flax. JAX offers NumPy-like tensor programming together with just-in-time compilation, automatic differentiation, and transformation-based parallel execution \cite{jaxrepo}. Flax provides the module abstractions used to define the model, including the compositional structure of the transformer blocks and the classifier head \cite{flaxrepo}. This choice of stack is particularly relevant for an N-dimensional implementation because tensor reshaping, permutation, and sharding are central both to generalized window attention and to the multi-GPU training workflow.

The evaluation uses two canonical datasets with very different input structure. CIFAR-10 is a standard 10-class image classification benchmark of \(32 \times 32\) RGB images \cite{krizhevsky2009cifar}. It provides a compact 2D workload suitable for validating whether the generalized code still behaves like a practical image classifier. ModelNet is a widely used dataset family for 3D object recognition \cite{wu20153dshapenets}. In this repository, the preserved 3D workload is a voxelized 40-class export that matches the model's volumetric input path rather than a raw mesh or point-cloud pipeline. The combination of these two datasets is useful precisely because they exercise the same codebase under distinct spatial dimensionalities.

This report does not attempt a broad survey of volumetric transformers or 3D recognition literature because that is not required to support the main claim. The relevant comparison is narrower: whether the implementation faithfully transfers the shifted-window principle from its original 2D formulation into a reusable N-dimensional JAX framework, and whether that implementation can be trained successfully on both 2D and 3D classification problems. The cited work above is sufficient to ground that question without overstating the novelty of the project.
